\clearpage
\section{Referências}

\begin{thebibliography}{99}

\bibitem{lamport1978}
LAMPORT, Leslie. \textit{Time, Clocks, and the Ordering of Events in a Distributed System}.
Communications of the ACM, v. 21, n. 7, p. 558--565, 1978.
DOI: \url{https://doi.org/10.1145/359545.359563}.
Texto consultado: \url{https://lamport.azurewebsites.net/pubs/time-clocks.pdf}.

\bibitem{ricart1981}
RICART, Glenn; AGRAWALA, Ashok K. \textit{An Optimal Algorithm for Mutual Exclusion in Computer Networks}.
Communications of the ACM, v. 24, n. 1, p. 9--17, 1981.
DOI: \url{https://doi.org/10.1145/358527.358537}.

\bibitem{garcia1982}
GARCIA-MOLINA, Hector. \textit{Elections in a Distributed Computing System}.
IEEE Transactions on Computers, v. C-31, n. 1, p. 48--59, 1982.
DOI: \url{https://doi.org/10.1109/TC.1982.1675885}.

\bibitem{python-asyncio}
PYTHON SOFTWARE FOUNDATION. \textit{Synchronization Primitives}.
Disponível em: \url{https://docs.python.org/3.12/library/asyncio-sync.html}.
Acesso em: 5 jul. 2026.

\bibitem{python-waitfor}
PYTHON SOFTWARE FOUNDATION. \textit{asyncio.wait\_for}.
Disponível em: \url{https://docs.python.org/3.12/library/asyncio-task.html#asyncio.wait_for}.
Acesso em: 5 jul. 2026.

\bibitem{python-time}
PYTHON SOFTWARE FOUNDATION. \textit{time.monotonic}.
Disponível em: \url{https://docs.python.org/3.12/library/time.html#time.monotonic}.
Acesso em: 5 jul. 2026.

\bibitem{fastapi}
FASTAPI. \textit{First Steps} e \textit{Lifespan Events}.
Disponível em: \url{https://fastapi.tiangolo.com/tutorial/first-steps/} e
\url{https://fastapi.tiangolo.com/advanced/events/}.
Acesso em: 5 jul. 2026.

\bibitem{uvicorn}
UVICORN. \textit{Settings}.
Disponível em: \url{https://www.uvicorn.org/settings/}.
Acesso em: 5 jul. 2026.

\bibitem{httpx}
HTTPX. \textit{Async Support}.
Disponível em: \url{https://www.python-httpx.org/async/}.
Acesso em: 5 jul. 2026.

\bibitem{pydantic}
PYDANTIC. \textit{Models}.
Disponível em: \url{https://docs.pydantic.dev/latest/concepts/models/}.
Acesso em: 5 jul. 2026.

\bibitem{pytest}
PYTEST. \textit{Documentation}.
Disponível em: \url{https://docs.pytest.org/en/stable/}.
Acesso em: 5 jul. 2026.

\bibitem{pytestasyncio}
PYTEST-ASYNCIO. \textit{Configuration}.
Disponível em: \url{https://pytest-asyncio.readthedocs.io/en/stable/reference/configuration.html}.
Acesso em: 5 jul. 2026.

\bibitem{dockerfile}
DOCKER. \textit{Dockerfile Reference}.
Disponível em: \url{https://docs.docker.com/reference/dockerfile/}.
Acesso em: 5 jul. 2026.

\bibitem{compose}
DOCKER. \textit{Compose File Reference: Services}.
Disponível em: \url{https://docs.docker.com/reference/compose-file/services/}.
Acesso em: 5 jul. 2026.

\end{thebibliography}
